Knowledge \& the web: exercise session 6

### 2015-11-22 exercise_6/ex6.tex

%\begin{figure}[htbp]
%  \centering
%  \includesvg[width = 0.7\textwidth]{decisiontreetitanic}
%  \caption{Decision tree with maximal depth of 3}
%\end{figure}

\section{?}

>>>>

Apart from \emph{rule learning} we also experimented witch decision trees. First we applied the standard decision tree in RapidMiner, it created a too complicated decision tree, as you can see in figure 1.
\begin{figure}[H]
  \centering
  \includesvg[width = 1.5\textwidth]{decisiontreetitanic_original}
  \caption{Original decision tree with maximal depth of 20}
\end{figure}
Next we limited the maximal depth of the decision tree to 3. This gave us figure 2, which is much more usefull.
\begin{figure}[H]
  \centering
  \includesvg[width = 1\textwidth]{decisiontreetitanic}
  \caption{Decision tree with maximal depth of 3}
\end{figure}

\section{Rule learning vs. Decision trees}

Settings for Rule learning 1:
\begin{itemize}
\item ...
\end{itemize}

Settings for Rule learning 2:
\begin{itemize}
\item ...
\end{itemize}

Settings for Decision tree 1:
\begin{itemize}
\item ...
\end{itemize}

Settings for Decision tree 2:
\begin{itemize}
\item ...
\end{itemize}

\begin{figure}[H]
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
• & Precision & Accuracy & Recall\\ 
\hline 
Rule learning 1 & • & • & • \\ 
\hline 
Rule learning 2 & • & • & • \\ 
\hline 
Decision tree 1 & • & • & • \\ 
\hline 
Decision tree 2 & • & • & • \\ 
\hline 
\end{tabular} 
\caption{Overview}
\end{figure}
